Streaming CityJSON datasets

### 2024-04-26 paper/main.tex
Add draft discussion

Notice that the dataset \textbf{3DBV} contains the ground that has been triangulated, and a few large areas are stored as \texttt{LandUse} and contain several triangles, this is the reason why the maximum memory use is larger than for other datasets.

@@

\begin{itemize}
  \item We have kept most of the structure of CityJSON so that parsers do not need to be adapted much.
  \item CityJSONSeq is an attractive alternative to CityJSON, in most uses it is better to use since it is compacter, processing it uses less memory and is faster.
  \item it opens up many possibilities for processing large 3dcm by using Unix pipes. A few of the tools developed for CityJSON are already reading/writing to stdin/stdout, so they can be chained together.
  \item cjseqview, cjseqval are two of them, but developing others to eg filter, calculate volumes or repair geometries would be trivial
  \item the nice part is that the tools do not need to be written in the same language, one pipeline can have tools built in Python and Rust and C++ and it all works nicely.
  \item extensions: these should be placed in the metadata or collection
\end{itemize}

Disadvantages:
\begin{itemize}
  \item  Software implementing CityJSON need to account for both regular CityJSON and CityJSONSeq.
  \item  In case of many, small, interconnecting CityObjects, a global vertex list would provide better compression than the separate vertex lists of the CityJSONFeatures.
  \item  Appearances (esp. Material) are relatively heavy objects with many properties. If an appearance is shared across most CityObjects, duplicating it in each Feature could negate the effect of small vertex indices and actually increase the file size compared to a regular CityJSON file. This is just theorizing, haven't tested.
\end{itemize}

@@

>>>>

Notice that the dataset \textbf{3DBV} contains the ground that has been triangulated, and a few large areas are stored as \texttt{LandUse} and contain a large amount of triangles; this is the reason why the maximum memory use is larger than for other datasets.

@@

@@

While CityJSONSeq was developed mostly for streaming large 3D city datasets, the fact that it has a much lower memory footprint and that it takes an order of magnitude less time to process (for some local operations) makes it an attractive alternative to CityJSON for general applications.

CityJSONSeq, being streamable, can be processed with \emph{Unix pipes} (also called \emph{pipelines}).
Pipelines allow us to chain several processes together, the output of a process becomes the input of the next one, and so on. 
Given 2 processes, the 2nd one can usually start before the 1st one has finished processing all the data.
This means in practice that the processing of a dataset can be performed by writing several programs that perform only small/atomic tasks; this makes the development and maintenance of code simpler.
Moreover, it allows us to develop the different programs in different languages. 
The pipeline used for preparing the datasets for this paper was actually a mix of Python (the program `cjio' and `cjdb') and Rust (`cjseq'), and another program written in C++ could easy be added.

The structure of CityJSONSeq is nearly the same as that of CityJSON, which means that supporting it requires a minimum amount of efforts since most of the code already existing can be used. 
We have already added support for it in a few of the open-source CityJSON tools (see \url{https://www.cityjson.org/software/}) and we will continue in the future.

% We developed CityJSONSeq mainly because we wanted to be able to stream large CityJSON files from a server.

% \begin{itemize}
%   % \item We have kept most of the structure of CityJSON so that parsers do not need to be adapted much.
%   % \item CityJSONSeq is an attractive alternative to CityJSON, in most uses it is better to use since it is compacter, processing it uses less memory and is faster.
%   \item it opens up many possibilities for processing large 3dcm by using Unix pipes. A few of the tools developed for CityJSON are already reading/writing to stdin/stdout, so they can be chained together.
%   \item cjseqview, cjseqval are two of them, but developing others to eg filter, calculate volumes or repair geometries would be trivial
%   \item the nice part is that the tools do not need to be written in the same language, one pipeline can have tools built in Python and Rust and C++ and it all works nicely.
%   \item extensions: these should be placed in the metadata or collection
% \end{itemize}

% Disadvantages:
% \begin{itemize}
%   \item  Software implementing CityJSON need to account for both regular CityJSON and CityJSONSeq.
%   \item  In case of many, small, interconnecting CityObjects, a global vertex list would provide better compression than the separate vertex lists of the CityJSONFeatures.
%   \item  Appearances (esp. Material) are relatively heavy objects with many properties. If an appearance is shared across most CityObjects, duplicating it in each Feature could negate the effect of small vertex indices and actually increase the file size compared to a regular CityJSON file. This is just theorizing, haven't tested.
% \end{itemize}
